Handbook streamFind: Backend

### 2023-03-08 README.Rmd
Updated webpage

The documentation and usage examples of the streamFind package can be found in the [reference page](https://ricardobachertdacunha.github.io/streamFind/reference/index.html) and [articles](https://ricardobachertdacunha.github.io/streamFind/articles/index.html) of the [webpage](https://ricardobachertdacunha.github.io/streamFind/index.html), respectively.

>>>>

The documentation and usage examples of the streamFind R package can be found in the [reference page](https://ricardobachertdacunha.github.io/streamFind/reference/index.html) and [articles](https://ricardobachertdacunha.github.io/streamFind/articles/index.html) of the [webpage](https://ricardobachertdacunha.github.io/streamFind/index.html), respectively.
